---
title       : Stocks Analysis
subtitle    : Simple Shiny App
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Simple Stock Analysis App

1. Loads historical prices for a given stock symbol
2. Calculates daily relative returns of stock prices
3. Can show time series of daily returns and histogram of returns distribution
4. Calculates autocorrelations of daily returns

--- .class #id 

## Loading Time Series

Load timeseries of specified stock symbols from yahoo finance using `quantmod` R package. The example below loads time series of Apple Inc. stock history starting 2010-01-01 and ending 2014-10-26. The corresponding plot is shown below.
```{r, echo=FALSE}
library(quantmod)
```
```{r}
aapl <- getSymbols("AAPL", auto.assign=FALSE, from='2010-01-01', to='2014-10-26')
```
```{r echo=FALSE, fig.width=10, fig.height=5, fig.align='center'}
plot(index(aapl), coredata(aapl)[,6], type='l', main="Stock Price History of Apple Inc.",
     xlab="Date", ylab="Adjusted Price")
```

---
## Relative Returns
Relative returns of stock prices time series $\{S_k\}$ are defined as: 
$$r_k = (S_k-S_{k-1})/S_{k-1}$$
The time series and distribution of daily relative returns of Apple Inc. are shown below:
```{r, echo =FALSE}
returns <- ROC(aapl); returns <- returns[complete.cases(returns)]
```
```{r echo=FALSE, fig.width=12, fig.height=5, fig.align='center'}
ret.df <- coredata(returns)

old_par <- par(mfrow=c(1,2))
plot(index(returns), ret.df[,6], type='l', main="History of Relative Returns",
     xlab="Date", ylab="Daily Returns", yaxt="n")
axis(2, at=pretty(ret.df[,6]), lab= paste0(pretty(ret.df[,6]) * 100, "%"), las=TRUE)

hist(ret.df[,6], breaks = 20, xlab="Relative Returns", xaxt="n", 
     main="Distribution of Relative Returns")
axis(1, at=pretty(ret.df[,6]), lab= paste0(pretty(ret.df[,6]) * 100, "%"), las=TRUE)  
par(old_par)

```


---
## Autocorrelations

In order to test whether daily returns are indepentent we can calculate autocorrelation using `acf()` R function.

```{r echo=FALSE, fig.width=10, fig.height=5, fig.align='center'}
acorr <- acf(ret.df[,6], plot=FALSE)
plot(acorr, main="Autocorrelation of daily returns", xlab="Lag",
      ylab="Autocorrelation")
```

